OECD TiVa LMIC GVCs

### 2015-04-21 OECD-TiVa-LMIC-GVCs.Rmd
working with plots

 ```{r}
 gvc_indicators %>%
  group_by(year, ic) %>%
  summarise(i2e = sum(fvax_ams_ik) / sum(exports_ik) ) %>%
  ggvis(~year, ~i2e, stroke = ~ic ) %>%
  layer_lines()
 ```

>>>>

## I2E

  ```{r, echo=FALSE}
 gvc_indicators %>%
  group_by(year, ic) %>%
  summarise(i2e = sum(fvax_ams_ik) / sum(exports_ik) ) %>%
  ggvis(~year, ~i2e, stroke = ~ic ) %>%
  layer_lines()
 ```
